---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
require(magrittr)
require(stp25output2)
require(stp25stat2)
require(stp25tools)
require(lattice)
```

# stp25output2

The scripts are used to generate reports as HTML, but also PDF via knit. Some of them are modified functions of R2HTML, texreg and htmlTable.

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/stp25stat2)](https://CRAN.R-project.org/package=stp25stat2)
<!-- badges: end -->

## Overview

-   Initialisation of new projects
    -   `Projekt()` and `End()` Initialises a new project and calls up the HTML page with the help of R2HTML.
-   Text and table formatting
    -   `Output` table formatting
    -   `Text`, `Head` and `Head1 ...` Writes HTML text.
-   Helper functions
    -   `SavePlot` Saves images to the working folder.

## Output formats

| File | Type            | Parameter       | which_output() |
|------|-----------------|-----------------|----------------|
| r    |                 |                 | text           |
| r    | Projekt("html") |                 | html           |
| r    | spin            | html_document   | markdown_html  |
| r    | spin            | pdf_document    | latex          |
| r    | spin            | word_document   | docx           |
| Rmd  |                 | html_document   | markdown_html  |
| Rmd  |                 | pdf_document    | latex          |
| Rmd  |                 | word_document   | docx           |
| Rmd  |                 | beamer          | latex          |
| Rmd  |                 | github_document | markdown_html  |

## Projekt

Initialises a new project.

```{r}
# devtools::install_github("stp4/stp25output")
 
Projekt("md", "Beispiel Projekt",
        datum = date()
        )

#stp25settings
set_opt(prozent=list(digits=c(1,0), style=2))

warpbreaks2 <- Label(warpbreaks,
                     breaks	=	"The number of breaks",
                     wool	=	"The type of wool",
                     tension	=	"The level of tension")
 

warpbreaks2 %>%
  Tbll_desc(breaks + tension ~ wool)

End()

```

### Usage

data.frame()

```{r output-data-frame, results='asis'}
set_opt(caption =TRUE)
which_output()
 
dat<- data.frame(
term = factor(c("A", "B", "C", "D")),
n = c(23, 14, 56, 2),
m = c("4.7 (2.4)", "4.1 (2.3)", "8.9 (3.6)", NA)
) 
attr(dat, "N") <- 56

dat  %>% Output("data.frame")
 

```

```{r}

Text("Hallo")
Text(dat, term, n, m,  include.levels=TRUE)
```

```{r output-matrix, results='asis'}

# matrix(c("a1","a2",3,4,5,6),
#                 nrow=2, byrow=TRUE,
#                 dimnames=list(gender=c("M", "F"),
#                               party=c( "Dem", "Ind", "Rep")))  #%>% Output("matrix()")

as.table(matrix(c("a1","a2",3,4,5,6),
                 nrow=2, byrow=TRUE,
                 dimnames=list(gender=c("M", "F"),
                               party=c( "Dem", "Ind", "Rep")))) %>% Output("as.table()")

```

```{r , results='asis'}
 
warpbreaks2 %>%
  Tbll_desc(breaks + tension + wool) %>% Output()


```

### Verschiedene Szenarien

```{r, include = FALSE}

df1 <- data.frame(
  term = c("A", "B", "C", "D"),
  n = c(23, 14, 56, 2),
  m = c("4.7 (2.4)", "4.1 (2.3)", "8.9 (3.6)", NA)
)

  attr(df1, "caption") <-  "Demo Ueberschrift"
  attr(df1, "note") <- "Note: Anmerkung"
  attr(df1, "N") <- 99
  set_opt(caption = TRUE)

```

```{r df-default, results='markup'}
#' default, results='markup'
df1 %>% Output()
```

```{r df-false, results='asis'}
#' default, results='asis'
df1 %>% Output()
```

```{r df-text, results='markup'}
#' results='markup'
df1 %>% Output(output="text")
```

```{r, df-md, results='asis'}
#' results='asis'
df1 %>% Output(output="markdown")
```

## xtable()
Convert an R object to an xtable object, which can then be printed as a LaTeX or HTML table

```{r, results='asis'}
 
require(xtable)
data(tli)
## Demonstrate aov
fm1 <- aov(tlimth ~ sex + ethnicty + grade + disadvg, data = tli)
fm1.table <- xtable(fm1)

Output(fm1.table)


```

```{r , results='markup'}

fm2 <- lm(tlimth ~ sex*ethnicty, data = tli)
fm2b <- lm(tlimth ~ ethnicty, data = tli)

#Output(xtable(anova(fm2b, fm2)), output="md")

```

## knitr::kable

```{r}
knitr::kable(
  df1, row.names = FALSE,
  format = "pandoc" 
)
```

```{r}

knitr::kable(
  df1, row.names = FALSE,
  format = "markdown" 
)

```

```{r}
knitr::kable(
  df1, row.names = FALSE,
  format = "pandoc" 
)
```

## Grafik settings

```{r, include=FALSE}
 
set.seed(2)
n <- 20 * 3 * 2
DF <- data.frame(
  n = runif(n, min = 1, max = 5),
  e = runif(n, min = 1, max = 5),
  o = runif(n, min = 1, max = 5),
  g = runif(n, min = 1, max = 5),
  a = runif(n, min = 1, max = 5),
  treatment = gl(3, n / 3, labels = c("UG1", "UG2", "KG"))[sample.int(n)],
  sex = gl(2, n / 2, labels = c("male", "female"))
)

```

```{r fig-default, fig.height=3, fig.width=4}
#set_lattice()
bwplot(e ~ treatment, DF)
# SavePlot()
```

```{r fig-ggplot, fig.height=3, fig.width=4}
#set_lattice_ggplot()
bwplot(e ~ treatment, DF)
# SavePlot()
```

```{r fig-bw, fig.height=3, fig.width=4}
#set_lattice_bw()
bwplot(e ~ treatment, DF)
# SavePlot()
```

## A few methods for making tables in rmarkdown

Quelle: <https://gist.github.com/benmarwick/8ad99f35d5e4caa06492>

<https://github.com/yihui/printr> <https://github.com/jalapic/simpletable> <https://github.com/renkun-ken/formattable>


```{r}
my_data <- head(iris)
names(my_data) <- c(letters[1:ncol(iris)])
```

```{r results='asis'}
library("knitr")
kable(my_data)
```

```{r results='asis'}
library("xtable")
print(xtable(my_data), type = "html", include.rownames=FALSE, html.table.attributes=list("border='0' cellpadding='5' "))
```

```{r, results = 'asis'}
library(xtable)
print(xtable(my_data), type = 'html')
```

```{r results = 'asis'}
library(xtable)
print(xtable(my_data), type = 'html', html.table.attributes = '')
```

```{r results='asis'}
library("pander")
pandoc.table(my_data)
```

```{r results='asis'}
library("pander")
pandoc.table(my_data, split.cells = 5)
```

```{r, results = 'asis'}
pander::panderOptions('table.split.table', 350)
pander::pandoc.table(my_data, style="rmarkdown")
```

```         
library("ascii")
print(ascii(my_data), type = 'pandoc')
```

```{r}
library("htmlTable")
htmlTable(my_data, col.rgroup = c("none", "#F7F7F7"))
```

```{r results='asis'}
library(hwriter)
hwrite(my_data, border=0)
```

This one is the most useful, and has a nice guide to customisation here: <http://www.ebi.ac.uk/~gpau/hwriter/>

```{r results='asis'}
library(hwriter)
cat(
  hwrite(
    my_data,
    border = 0,
    center = TRUE,
    table.frame = 'void',
    width = '300px',
    table.style = 'padding: 50px',
    row.names = FALSE,
    row.style = list('font-weight:bold')
  )
)
```
